\section{Courses}
\label{Courses}
Courses that are taken for the graduate education are listed below. Each student is required to pass 45 points for licentiate thesis.
\begin{center}
	\begin{tabular}{| l | l | l |}
		\hline
		\textbf{Course Name} & \textbf{Credits} & \textbf{Status} \\ \hline
		Case Based Reasoning & 15 & Completed \\ \hline
		Estimation Theory & 10.0 & Completed \\ \hline
		Antenna Theory, PhD Course I & 8.0 & Completed \\ \hline
		Professional Ethics & 7.5 & TBD \\ \hline
		Scientific Writing with LaTeX & 7.5 & TBD \\
		\hline
		Reseach methodology & 7.5 & Completed \\
		\hline
		Research Planning & 3.0 & Completed \\ \hline
		Training School on UWB Antennas, Technologies and Applications & 1.5 & Completed \\ \hline
		\multicolumn{1}{r}{\textbf{Sum =}}&\multicolumn{2}{l}{\textbf{60}} \\
	\end{tabular}
\end{center}

\section{Conferances and Workshops}
I attended following conferences during my graduate education: 
\label{Conferances}
\begin{itemize}
	\item 2014 IEEE International Conference on Ultra-WideBand (ICUWB)
	
	I attended this conference in Paris and I got acquainted with the experts in the field and get a holistic view of state of the art research in the field.
	\item Training School on UWB Antennas, Technologies and Applications - Karlsruhe, Germany, April 20-24
	
	This training school was arranged by European school of antennas and COST action TU1208 for ground penetrating radar(GPR). The training was giving an insight to UWB antennas and system by the prominent researchers in the field.  
	\item 2016 IEEE International Conference on Ubiquitous Wireless Broadband (ICUWB)
	I attended this conference to present paper A.
\end{itemize}



\subsection{Third cycle outcome}

\subsubsection{Knowledge and understanding / Research Area}
 \textbf{1.1a Knowledge and understanding of the research area}

I have taken graduate courses (see \ref{Courses}), attended one licentiate and one PhD defense and presentation. I attended a training school and conferences (see \ref{Conferances}).

 \textbf{1.1b Specialist knowledge in a defined part of the research area}
 
 I have published peer reviewed- scientific papers and participated in international workshops and conferences.
 
 \textbf{1.1c Deep knowledge of research methods in general, and of research methods in the specific research area}

I have taken research methods and research planning courses.

\subsubsection{Competence and Skills}
\textbf{2.1a Critically and independently identify and formulate research questions}

I have written and published scientific articles and papers as first author and main contributor (see \ref{papers}).

\textbf{2.1b Contribute to the development of knowledge}
I have performed studies and experiments and published the results in scientific articles and papers (see \ref{papers}).

\textbf{2.2 Orally and in writing present and discuss research results with the national and international scientific community, and the society in general}
I have written and published scientific articles and attended with own contributions at international conference(see \ref{papers}).

\textbf{2.3 Independently conduct research and development}
I have been the main responsible for this research and published peer reviewed scientific articles. 

\subsubsection{Judgement and Approach}

\textbf{3.1 Demonstrate ability to make ethical assessments in own research}

I have planned my own research. I took  research ethics, research methods and research planning courses.

\textbf{3.2 Demonstrate understanding of science's role and use in society, including its possibilities and limitations, and responsibility of its use}
If this technique is going to be used in application which are protecting humans from machineries it's limitations shall be fully explored because every decisions based on the sensor data can be either costly in case of false alarm or injuries and loss of lives in case of missed target.

\textbf{3.3 Identify one's need of further knowledge and take responsibility for one's learning} 

???



\subsection{Time plan}
This is the time plan up to the licentiate seminar.
\begin{itemize}
	\item Licentiate proposal - 24 November, 2016.
	\item Professional Ethics course to be finished - Fall 2016.
	\item Scientific Writing Using LaTeX course to be finished - Fall 2016.
	\item Paper C - fall 2016. Journal paper.
	\item Application for licentiate seminar - 22 March, 2017.
	\item Licentiate thesis, first draft - Jun, 2017.
	\item Licentiate thesis, camera ready - August, 2017.
	\item Licentiate seminar - September, 2017.
\end{itemize}


\subsection{Thesis opponent and committee}